Non-kissing and non-crossing complexes \\ for gentle algebras

### 2018-05-30 draft/accordionComplexSurfaces.tex
Definition of Koszul dual.

% ALGEBRA
\newcommand{\Hom}[1]{\operatorname{{\rm Hom}}_{#1}}
\newcommand{\Ext}[1]{\operatorname{{\rm Ext}}_{#1}}
\newcommandx{\AR}[1][1=\bar Q]{\mathrm{AR}(#1)} % Auslander-Reiten quiver
\newcommandx{\tTC}[1][1=\bar Q]{\mathcal{K}^{\textrm{s$\tau$-tilt}}(#1)} % tau-tilting complex
\newcommand{\rep}{\operatorname{{\rm rep}}}
\newcommand{\proj}{\operatorname{{\rm proj}}}

@@

\begin{proposition}
\label{prop:dualityKoszul1}
For two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of an oriented surface, the quivers~$\bar Q_{\dissection}$ and~$\bar Q_{\dissection\dual}$ are Koszul duals.
\vincent{Here I mean that the gentle algebras are Koszul duals. We need to define that somewhere and discuss it on gentle quivers.}
\end{proposition}

>>>>

% ALGEBRA
\newcommand{\Hom}[1]{\operatorname{{\rm Hom}}_{#1}}
\newcommand{\Ext}[1]{\operatorname{{\rm Ext}}_{#1}}
\newcommandx{\AR}[1][1=\bar Q]{\mathrm{AR}(#1)} % Auslander-Reiten quiver
\newcommandx{\tTC}[1][1=\bar Q]{\mathcal{K}^{\textrm{s$\tau$-tilt}}(#1)} % tau-tilting complex
\newcommand{\rep}{\operatorname{{\rm rep}}}
\newcommand{\proj}{\operatorname{{\rm proj}}}
\newcommand{\koszul}{^!} % duality

@@

\begin{example}
 An example on the annulus...
\end{example}

\begin{definition}
\label{defi:koszulDual}
The \defn{Koszul dual} of a gentle bound quiver~$\bar Q = (Q,I)$ is the bound quiver~$\bar Q\koszul = (Q\koszul, I\koszul)$ defined as follows:
\begin{itemize}
 \item the quiver~$Q\koszul$ is equal to~$Q$;
 \item the ideal~$I\koszul$ is generated by the paths of length two in~$Q$ that do not appear in~$I$.
\end{itemize}
\end{definition}
\pierreguy{Justify this definition.}
Note that~$\bar Q\koszul$ is gentle, and that~$(\bar Q\koszul)\koszul = \bar Q$.

\begin{proposition}
\label{prop:dualityKoszul1}
Let~$\dissection$ and~$\dissection\dual$ be two dual cellular dissections of a marked surface~$(\surface, V\sqcup V\dual)$.
The bound quivers~$\bar Q_{\dissection}$ and~$\bar Q_{\dissection\dual}$ are Koszul dual to each other.
\end{proposition}
